Exploratory data analysis

### 2019-06-15 analysis/eda.Rmd
update reports

```{r eda-17}
boxplot_defol <- vi_data_plot %>%
  group_by(plot) %>%
  ggboxplot(
    x = "plot", y = "defoliation", color = "plot",
    add = "jitter", add.params = list(size = "defoliation")
  ) +
  scale_size(range = c(0.5, 0.5)) +
  annotate("text",
    label = expression(bold(atop("n = 479", bar(x) ~ "= 55.96"))), x = 1,
    y = 112, size = 3, colour = "#BC3C29", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 451", bar(x) ~ "= 13.54"))), x = 2,
    y = 112, size = 3, colour = "#0072B5", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 300", bar(x) ~ "= 68.44"))), x = 3,
    y = 112, size = 3, colour = "#E18727", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 529", bar(x) ~ "= 69.22"))), x = 4,
    y = 112, size = 3, colour = "#20854E", fontface = 2
  ) +
  scale_color_nejm() +
  theme(legend.position = "none") +
  labs(y = "Total defoliation per tree (%)", x = "Plot")
boxplot_defol
```

@@

>>>>

```{r defoliation-distribution-plot, dev = c("png", "pdf")}
boxplot_defol <- vi_data_plot %>%
  group_by(plot) %>%
  ggboxplot(
    x = "plot", y = "defoliation", color = "plot",
    add = "jitter", add.params = list(size = "defoliation")
  ) +
  scale_size(range = c(0.5, 0.5)) +
  annotate("text",
    label = expression(bold(atop("n = 479", bar(x) ~ "= 55.96"))), x = 1,
    y = 112, size = 3, colour = "#BC3C29", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 451", bar(x) ~ "= 13.54"))), x = 2,
    y = 112, size = 3, colour = "#0072B5", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 300", bar(x) ~ "= 68.44"))), x = 3,
    y = 112, size = 3, colour = "#E18727", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 529", bar(x) ~ "= 69.22"))), x = 4,
    y = 112, size = 3, colour = "#20854E", fontface = 2
  ) +
  scale_color_nejm() +
  theme(legend.position = "none") +
  labs(y = "Total defoliation per tree (%)", x = "Plot")
boxplot_defol
```

@@

```{r echo = FALSE}
file_move(list.files(here("docs/figure/eda.Rmd/"), 
                     pattern = "defoliation-distribution-plot", 
                     full.names = TRUE),
          here("code/98-paper/journal/"))
```
